Uncovering Distributed System Bugs\\ during Testing (not Production!) -- draft title

### 2015-08-17 paper.tex
update

@@

@@

\subsection{Distributed Extent Management System}

@@

Draft

>>>>

\section{Overview}
\label{sec:overview}

How cheng was testing his code before and how after -- high level, pretty picture

%\input{overview}

@@

Dependency injection pattern

\section{Methodology}
\label{sec:methodology}

%\input{methodology}

Very simple running example (maybe some master and some worker nodes) and describe how its environment is modeled and its tested.

@@

% cheng to review
\subsection{Distributed Extent Management System}

@@

Paragraph that says what will be discussed in evaluation and what are the results (very short)

\subsection{Experimental Setup}

\subsection{Benchmarks}

Benchmarks that are not production code (e.g. multipaxos) that can be used to evaluate testing

Cheng's case study with the actual bug

Matt's case study with injected bugs

\subsection{Stressing testing vs Systematic testing}

Comparison of traditional stress testing VS what we do with \psharp

How long you had to run the test to find the bug (if you can find it) and how long are the traces

How easy it is to pinpoint the error using the \psharp traces, comparing to traditional stress testing

Effort required to use the system
